\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{lscape}
\usepackage{caption}

\author{Markus Meier}
\title{Heuristic Analysis}
\begin{document}
\section{Heuristic Analysis}
\subsection{Non-heuristic search algorithms}
The results for the three non-heuristic search algorithsm breadth first search, depth first graph search and uniform cost search are shown in the table below.
In general the problem difficulty increases from problem 1 over problem 2 to problem 3.
As expected, the depth first graph search does not produce optimal solutions. However, it is the fastest method.
The breadth first search and the uniform cost search find optimal solutions.
The breadth first search is slightly faster than the uniform cost search.

\subsection{Heuristic search algorithms}
We compare A* searches without heuristics (h1), with the ignore preconditions heuristic and with the pg levelsum. All three methods find optimal solutions. The fastest heuristic is with the pg levelsum.

Considering the increasing problem difficulty, A* with the pg levelsum heuristic is the method that also scales best.

\subsection{Summary}
The A* search with the pg levelsum heuristic finds in all three problem cases in the optimal solution. The A* search is also the fastest method. Therefore, I would recommend to use this method. However, for real world problems with several thousands or millions of entities, the method might be still too slow.



\begin{landscape}
\begin{center}
\captionof{table}{Non-heuristic searches}
\begin{tabular}[pos]{c|c|c|c|c|c|c}
problem   & method                   & expansions & goal tests & new nodes & plan length & time \\
Problem 1 & breadth first search     & 43         & 56 & 180   & 6  & 0.53 \\
Problem 1 & depth first graph search & 21         & 22 & 84    & 20 & 0.25 \\
Problem 1 & uniform cost search      & 55         & 57 & 224   & 6  & 0.73 \\

Problem 2 & breadth first search     & 3343       & 4609 & 30509 & 9   & 308.91 \\
Problem 2 & depth first graph search & 624        & 625  & 5602  & 619 & 54.10 \\
Problem 2 & uniform cost search      & 4853       & 4853 & 44041 & 9   & 434.89 \\

Problem 3 & breadth first search     & 14663      & 18098 & 129631 & 12   & 1547.98 \\
Problem 3 & depth first graph search & 408        & 409   & 3364   & 392  & 39.06 \\
Problem 3 & uniform cost search      & 18223      & 18225 & 159618 & 12   & 1812.65 \\
\end{tabular}
\end{center}

\begin{center}
\captionof{table}{A* search with heuristics}
\begin{tabular}[pos]{c|c|c|c|c|c|c}
problem   & method                   & expansions & goal tests & new nodes & plan length & time \\
Problem 1 & astar search with h1     & 55         & 57         & 224       & 6           & 0.61 \\
Problem 1 & astar search with ignore preconditions     & 41         & 43         & 170       & 6           & 0.64 \\
Problem 1 & astar search with pg levelsum     & 11         & 13         & 50       & 6           & 0.59 \\

Problem 2 & astar search with h1     & 4853         & 4855         & 44041       & 9           & 435.43 \\
Problem 2 & astar search with ignore preconditions     & 1450         & 1452         & 13303       & 9           & 163.85 \\
Problem 2 & astar search with pg levelsum     & 86         & 88         & 841       & 9           & 14.70 \\

Problem 3 & astar search with h1     & 18223         & 18225         & 159618       & 12           & 1902.70 \\
Problem 3 & astar search with ignore preconditions     & 5040         & 5042         & 44944       & 12           & 640.72 \\
Problem 3 & astar search with pg levelsum     & 318         & 320         & 2934       & 12           & 67.02 \\
        
\end{tabular}
\end{center}
\end{landscape}





\end{document}